Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions

### 2022-06-30 Resubmission/Laws_C2H_v2.tex
v3

These interactions spread the electronic orgin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels. Therefore, instead of assigning a defined origin, the peaks observed in experimental spectra may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
\begin{equation}
\Psi_f = \sum_\xi \psi_e^\xi \sum_k C_{fk}^\xi\phi_{fkm}^\xi,
\label{eq:3} 
\end{equation}
where $\psi_e^\xi$ is the diabatic electronic wavefunction, and $\phi_{fkm}^\xi$ is the spin-rovibrational wavefunction. $\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).

@@

\section{Methods}
\subsection{Experimental Procedure}
Details of the HR-PEI spectrometer are given in Refs~\onlinecite{cav07} and~\onlinecite{dev17}. Briefly, ethynyl ions C$_2$H$^-$ and C$_2$D$^-$ were produced in a pulsed-jet discharge of pure ethylene (C$_2$H$_4$/C$_2$D$_4$) gas, and subsequently mass isolated over a 2m-long time of flight region~\cite{ded01}. Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic (355~nm) of a Nd:YAG laser. Higher electron counts were also obtained with the direct use of the third and fourth harmonics (266~nm) from the Nd:YAG laser. The detached electrons are mapped onto a micro-channel plate detector using a modified Velocity Map Imaging (VMI) lens. Each detachment event is imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer within the 10Hz repetition rate of the laser and processed in real time to identify electron events, centroiding each position to a subpixel accuracy.

@@

\subsection{Computational Details}
Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}. The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}). EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states, making it well suited to the study of photodetachment~\cite{gul21b,and22,bar07}. The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.

@@

The photdetachment transitions of C$_2$H$^-$ and C$_2$D$^-$ were calculated using the parameters in Table~\ref{tab:1} and the xsim package of CFOUR~\cite{dev20}. The xsim module projects the Hamiltonian (Eq.~\ref{eq:5}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum. In this simulation the transition moments for the two ionisation processes are assumed to be equal. The calculated transitions are shown in Figs.~\ref{fig:2}(a) and (b) alongside the experimental photoelectron spectra measured at 355~nm. Transitions with $\Sigma$ vibronic symmetry are shown in blue and transitions with $\Pi$ symmetry are in orange. The positions of the $\tilde{A} ^2\Pi$ transitions have been shifted by 500~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy ($\Delta^A_0-\Delta^X_0$ in Table~\ref{tab:1}).

@@

\section{Conclusions} 
High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ have been recorded at multiple wavelengths between 355~nm and 266~nm, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain. The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels. By transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated. A KDC Hamiltonian was constructed, and parametrised using the high-level EOM-CCSDT quantum chemical approach and the quasidiabatic ansatz. The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ reproduce the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin. Photoelectron anisotropy parameters were also measured for dominant transitions, at a range of wavelengths. The sign $(+/-)$ of the electron anisotropy parameter, when compared with the calculated vibronic symmetry, allowed even weak or partially resolved transitions to be assigned.

The excellent agreement between the experimental and calculated spectra of this work
demonstrate that electronic spectra, complicated by vibronic coupling effects, may still be accurately simulated by using a quasidiabatic treatment, as parametrised by appropriate quantum chemical methodology. This approach may be applied to larger, less well known, C$_{2n}$H species, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers. It is especially encouraging that the fairly modest parametrisation used here works so well for C$_2$H, as this bodes well for its extension to larger systems.

@@

\bibliography{Laws_C2H}

>>>>

These interactions spread the electronic origin of the $\tilde{A}\,^2\Pi$ state over several vibronic levels. Therefore, instead of assigning a defined origin, the peaks observed in experimental spectra may be assigned to coupled admixtures of vibronic transitions involving the three potential energy surfaces,
\begin{equation}
\Psi_f = \sum_\xi \psi_e^\xi \sum_k C_{fk}^\xi\phi_{fkm}^\xi,
\label{eq:3} 
\end{equation}
where $\psi_e^\xi$ is the diabatic electronic wavefunction, and $\phi_{fkm}^\xi$ is the spin-rovibrational wavefunction. $\xi$ represents the electronic states used in the expansion ($\xi=\Sigma^+(1A'),~\Pi^+(2A'),~\Pi^-(1A'')$).

@@

\section{Methods}
\subsection{Experimental Procedure}
Details of the HR-PEI spectrometer are given in Refs.~\onlinecite{cav07} and~\onlinecite{dev17}. Briefly, ethynyl ions C$_2$H$^-$ and C$_2$D$^-$ were produced in a pulsed-jet discharge of pure ethylene (C$_2$H$_4$/C$_2$D$_4$) gas, and subsequently mass isolated over a 2m-long time of flight region~\cite{ded01}. Electrons were detached using a tuneable Continuum Sunlite Ex Optical Parametric Oscillator (OPO) pumped with the third harmonic (355~nm) of a Nd:YAG laser. Higher electron counts were also obtained with the direct use of the third and fourth harmonics (266~nm) from the Nd:YAG laser. The detached electrons are mapped onto a micro-channel plate detector using a modified Velocity Map Imaging (VMI) lens. Each detachment event is imaged by a 2048x2048 monochrome CCD camera (PCO 2000), with each frame transferred to a computer within the 10Hz repetition rate of the laser and processed in real time to identify electron events, centroiding each position to a subpixel accuracy.

@@

\subsection{Computational Details}
Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}. The equation-of-motion ionized-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}). EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionized states, making it well suited to the study of photodetachment~\cite{gul21b,and22,bar07}. The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.

@@

The photdetachment transitions of C$_2$H$^-$ and C$_2$D$^-$ were calculated using the parameters in Table~\ref{tab:1} and the xsim package of CFOUR~\cite{dev20}. The xsim module projects the Hamiltonian (Eq.~\ref{eq:5}) onto a vibrational basis, which is then diagonalized using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum. In this simulation the transition moments for the two ionization processes are assumed to be equal. The calculated transitions are shown in Figs.~\ref{fig:3}(a) and (b) alongside the experimental photoelectron spectra measured at 355~nm. Transitions with $\Sigma$ vibronic symmetry are shown in blue and transitions with $\Pi$ symmetry are in orange. The positions of the $\tilde{A} ^2\Pi$ transitions have been shifted by 500~cm$^{-1}$ to account for the EOMIP-CCSDT calculations overestimating the effective Term energy ($\Delta^A_0-\Delta^X_0$ in Table~\ref{tab:1}).

@@

\section{Conclusions} 
High-resolution photoelectron images of C$_2$H$^-$ and C$_2$D$^-$ have been recorded at multiple wavelengths between 355~nm and 266~nm, to investigate vibronic coupling effects in the simplest C$_{2n}$H carbon monohydride chain. The interplay of pseudo Jahn-Teller and Renner Teller coupling between the close lying $\tilde{X}^2\Sigma^+$ and $\tilde{A}^2\Pi$ states results in a complex vibronic spectrum near the $\tilde{A}$ state surface, with the electronic origin split over multiple admixed levels. By transforming to a quasidiabatic representation, the effect of these coupling interactions may be accurately simulated. A KDC Hamiltonian was constructed, and parametrized using the high-level EOM-CCSDT quantum chemical approach and the quasidiabatic ansatz. The resulting simulated photoelectron spectra of C$_2$H$^-$ and C$_2$D$^-$ reproduce the experimental data, particularly in the complex energy region of the $\tilde{A}$ state origin. Photoelectron anisotropy parameters were also measured for dominant transitions, at a range of wavelengths. The sign $(+/-)$ of the electron anisotropy parameter, when compared with the calculated vibronic symmetry, allowed even weak or partially resolved transitions to be assigned.

The excellent agreement between the experimental and calculated spectra of this work
demonstrate that electronic spectra, complicated by vibronic coupling effects, may still be accurately simulated by using a quasidiabatic treatment, as parametrized by appropriate quantum chemical methodology. This approach may be applied to larger, less well known, C$_{2n}$H species, which may help guide the search for these molecules in astronomical studies, and help identify potential DIB carriers. It is especially encouraging that the fairly modest parametrization used here works so well for C$_2$H, as this bodes well for its extension to larger systems.

@@

%\bibliography{Laws_C2H}
%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{98}%
	\makeatletter
	\providecommand \@ifxundefined [1]{%
		\@ifx{#1\undefined}
	}%
	\providecommand \@ifnum [1]{%
		\ifnum #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \@ifx [1]{%
		\ifx #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \natexlab [1]{#1}%
	\providecommand \enquote  [1]{``#1''}%
	\providecommand \bibnamefont  [1]{#1}%
	\providecommand \bibfnamefont [1]{#1}%
	\providecommand \citenamefont [1]{#1}%
	\providecommand \href@noop [0]{\@secondoftwo}%
	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
	\providecommand \@@startlink[1]{}%
	\providecommand \@@endlink[0]{}%
	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
	\providecommand \urlprefix  [0]{URL }%
	\providecommand \Eprint [0]{\href }%
	\providecommand \doibase [0]{http://dx.doi.org/}%
	\providecommand \selectlanguage [0]{\@gobble}%
	\providecommand \bibinfo  [0]{\@secondoftwo}%
	\providecommand \bibfield  [0]{\@secondoftwo}%
	\providecommand \translation [1]{[#1]}%
	\providecommand \BibitemOpen [0]{}%
	\providecommand \bibitemStop [0]{}%
	\providecommand \bibitemNoStop [0]{.\EOS\space}%
	\providecommand \EOS [0]{\spacefactor3000\relax}%
	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
	\let\auto@bib@innerbib\@empty
	%</preamble>
	\bibitem [{\citenamefont {Kiefer}, \citenamefont {Von~Drasek},\ and\
		\citenamefont {Von~Drasek}(1990)}]{kie90}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
			{Kiefer}}, \bibinfo {author} {\bibfnamefont {W.~A.}\ \bibnamefont
			{Von~Drasek}}, \ and\ \bibinfo {author} {\bibfnamefont {W.~A.}\ \bibnamefont
			{Von~Drasek}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
				mechanism of the homogeneous pyrolysis of acetylene},}\ }\href {\doibase
		https://doi.org/10.1002/kin.550220710} {\bibfield  {journal} {\bibinfo
			{journal} {International Journal of Chemical Kinetics}\ }\textbf {\bibinfo
			{volume} {22}},\ \bibinfo {pages} {747--786} (\bibinfo {year}
		{1990})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Kiefer}\ \emph {et~al.}(1992)\citenamefont {Kiefer},
		\citenamefont {Sidhu}, \citenamefont {Kern}, \citenamefont {Xie},
		\citenamefont {Chen},\ and\ \citenamefont {Harding}}]{kie92}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
			{Kiefer}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Sidhu}},
		\bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont {Kern}}, \bibinfo
		{author} {\bibfnamefont {K.}~\bibnamefont {Xie}}, \bibinfo {author}
		{\bibfnamefont {H.}~\bibnamefont {Chen}}, \ and\ \bibinfo {author}
		{\bibfnamefont {L.~B.}\ \bibnamefont {Harding}},\ }\bibfield  {title}
	{\enquote {\bibinfo {title} {The homogeneous pyrolysis of acetylene ii: The
				high temperature radical chain mechanism},}\ }\href {\doibase
		10.1080/00102209208951815} {\bibfield  {journal} {\bibinfo  {journal}
			{Combustion Science and Technology}\ }\textbf {\bibinfo {volume} {82}},\
		\bibinfo {pages} {101--130} (\bibinfo {year} {1992})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Boullart}\ \emph {et~al.}(1996)\citenamefont
		{Boullart}, \citenamefont {Devriendt}, \citenamefont {Borms},\ and\
		\citenamefont {Peeters}}]{bou96}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
			{Boullart}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Devriendt}},
		\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Borms}}, \ and\ \bibinfo
		{author} {\bibfnamefont {J.}~\bibnamefont {Peeters}},\ }\bibfield  {title}
	{\enquote {\bibinfo {title} {{Identification of the Sequence CH($^2\Pi$) +
					C$_2$H$_2$ $\rightarrow$ C$_3$H$_2$ + H (and C$_3$H + H$_2$) Followed by
					C$_3$H$_2$ + O $\rightarrow$ C$_2$H + HCO (or H + CO) as C$_2$H Source in
					C$_2$H$_2$/O/H Atomic Flames}},}\ }\href {\doibase 10.1021/jp951995o}
	{\bibfield  {journal} {\bibinfo  {journal} {The Journal of Physical
				Chemistry}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo {pages} {998--1007}
		(\bibinfo {year} {1996})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Irvine}, \citenamefont {Ohishi},\ and\ \citenamefont
		{Kaifu}(1991)}]{wil91}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~M.}\ \bibnamefont
			{Irvine}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ohishi}}, \
		and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Kaifu}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {Chemical abundances in cold, dark
				interstellar clouds},}\ }\href {\doibase
		https://doi.org/10.1016/0019-1035(91)90120-I} {\bibfield  {journal} {\bibinfo
			{journal} {Icarus}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo {pages}
		{2--6} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Vuitton}\ \emph {et~al.}(2001)\citenamefont
		{Vuitton}, \citenamefont {Scemama}, \citenamefont {Gazeau}, \citenamefont
		{Chaquin},\ and\ \citenamefont {B\'{e}nilan}}]{vui01}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
			{Vuitton}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Scemama}},
		\bibinfo {author} {\bibfnamefont {M.-C.}\ \bibnamefont {Gazeau}}, \bibinfo
		{author} {\bibfnamefont {P.}~\bibnamefont {Chaquin}}, \ and\ \bibinfo
		{author} {\bibfnamefont {Y.}~\bibnamefont {B\'{e}nilan}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {{IR and UV spectroscopic data for
					polyynes: Predictions for long carbon chain compounds in Titan's
					atmosphere}},}\ }\href {\doibase
		https://doi.org/10.1016/S0273-1177(01)00059-X} {\bibfield  {journal}
		{\bibinfo  {journal} {Advances in Space Research}\ }\textbf {\bibinfo
			{volume} {27}},\ \bibinfo {pages} {283--288} (\bibinfo {year}
		{2001})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Wilson}\ and\ \citenamefont {Atreya}(2003)}]{wil03}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
			{Wilson}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
			{Atreya}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Chemical sources
				of haze formation in {Titan's} atmosphere},}\ }\href {\doibase
		https://doi.org/10.1016/j.pss.2003.06.003} {\bibfield  {journal} {\bibinfo
			{journal} {Planetary and Space Science}\ }\textbf {\bibinfo {volume} {51}},\
		\bibinfo {pages} {1017--1033} (\bibinfo {year} {2003})},\ \bibinfo {note}
	{surfaces and Atmospheres of the Outer Planets their Satellites and Ring
		Systems}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Dobrijevic}\ \emph {et~al.}(2016)\citenamefont
		{Dobrijevic}, \citenamefont {Loison}, \citenamefont {Hickson},\ and\
		\citenamefont {Gronoff}}]{dob16}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Dobrijevic}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Loison}},
		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Hickson}}, \ and\
		\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Gronoff}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {{1D}-coupled photochemical model of
				neutrals, cations and anions in the atmosphere of {Titan}},}\ }\href
	{\doibase https://doi.org/10.1016/j.icarus.2015.12.045} {\bibfield  {journal}
		{\bibinfo  {journal} {Icarus}\ }\textbf {\bibinfo {volume} {268}},\ \bibinfo
		{pages} {313 -- 339} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Jackson}\ \emph {et~al.}(1996)\citenamefont
		{Jackson}, \citenamefont {Blunt}, \citenamefont {Lin}, \citenamefont {Green},
		\citenamefont {Olivera}, \citenamefont {Fink}, \citenamefont {Bao},
		\citenamefont {Urdahl}, \citenamefont {Mohammad},\ and\ \citenamefont
		{Zahedi}}]{jac96}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~M.}\ \bibnamefont
			{Jackson}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Blunt}},
		\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Lin}}, \bibinfo {author}
		{\bibfnamefont {M.}~\bibnamefont {Green}}, \bibinfo {author} {\bibfnamefont
			{G.}~\bibnamefont {Olivera}}, \bibinfo {author} {\bibfnamefont {W.~H.}\
			\bibnamefont {Fink}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
			{Bao}}, \bibinfo {author} {\bibfnamefont {R.~S.}\ \bibnamefont {Urdahl}},
		\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Mohammad}}, \ and\
		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Zahedi}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {Non-adiabatic interactions in excited
				{C$_2$H} molecules and their relationship to {C$_2$} formation in comets},}\
	}\href {\doibase 10.1007/BF00644319} {\bibfield  {journal} {\bibinfo
			{journal} {Astrophysics and Space Science}\ }\textbf {\bibinfo {volume}
			{236}},\ \bibinfo {pages} {29--47} (\bibinfo {year} {1996})}\BibitemShut
	{NoStop}%
	\bibitem [{\citenamefont {{Ziurys}}\ \emph {et~al.}(1982)\citenamefont
		{{Ziurys}}, \citenamefont {{Saykally}}, \citenamefont {{Plambeck}},\ and\
		\citenamefont {{Erickson}}}]{ziu82}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont
			{{Ziurys}}}, \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
			{{Saykally}}}, \bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
			{{Plambeck}}}, \ and\ \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont
			{{Erickson}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Detection
					of the N=3-2 transition of CCH in Orion and determination of the molecular
					rotational constants}},}\ }\href {\doibase 10.1086/159709} {\bibfield
		{journal} {\bibinfo  {journal} {The Astrophysical Journal}\ }\textbf
		{\bibinfo {volume} {254}},\ \bibinfo {pages} {94--99} (\bibinfo {year}
		{1982})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2009)\citenamefont {Gupta},
		\citenamefont {Gottlieb}, \citenamefont {McCarthy},\ and\ \citenamefont
		{Thaddeus}}]{gup09}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
			{Gupta}}, \bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont {Gottlieb}},
		\bibinfo {author} {\bibfnamefont {M.~C.}\ \bibnamefont {McCarthy}}, \ and\
		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {A survey of {C$_4$H, C$_6$H, and
					C$_6$H$^-$ with the Green Bank Telescope}},}\ }\href {\doibase
		10.1088/0004-637x/691/2/1494} {\bibfield  {journal} {\bibinfo  {journal} {The
				Astrophysical Journal}\ }\textbf {\bibinfo {volume} {691}},\ \bibinfo {pages}
		{1494--1500} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Beuther}\ \emph {et~al.}(2008)\citenamefont
		{Beuther}, \citenamefont {Semenov}, \citenamefont {Henning},\ and\
		\citenamefont {Linz}}]{beu08}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
			{Beuther}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Semenov}},
		\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Henning}}, \ and\
		\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Linz}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {Ethynyl ({C$_2$H}) in massive star
				formation: Tracing the initial conditions?}}\ }\href
	{http://stacks.iop.org/1538-4357/675/i=1/a=L33} {\bibfield  {journal}
		{\bibinfo  {journal} {The Astrophysical Journal Letters}\ }\textbf {\bibinfo
			{volume} {675}},\ \bibinfo {pages} {L33} (\bibinfo {year}
		{2008})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2015)\citenamefont {Jiang},
		\citenamefont {Liu}, \citenamefont {Zhang}, \citenamefont {Wang},
		\citenamefont {Zhang}, \citenamefont {Li}, \citenamefont {Gao},\ and\
		\citenamefont {Gu}}]{jia15}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.-J.}\ \bibnamefont
			{Jiang}}, \bibinfo {author} {\bibfnamefont {H.~B.}\ \bibnamefont {Liu}},
		\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Zhang}}, \bibinfo
		{author} {\bibfnamefont {J.}~\bibnamefont {Wang}}, \bibinfo {author}
		{\bibfnamefont {Z.-Y.}\ \bibnamefont {Zhang}}, \bibinfo {author}
		{\bibfnamefont {J.}~\bibnamefont {Li}}, \bibinfo {author} {\bibfnamefont
			{Y.}~\bibnamefont {Gao}}, \ and\ \bibinfo {author} {\bibfnamefont
			{Q.}~\bibnamefont {Gu}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
			{{{SMA} Observations of C$_2$H in High-Mass Star-Forming Regions}},}\ }\href
	{\doibase 10.1088/0004-637x/808/2/114} {\bibfield  {journal} {\bibinfo
			{journal} {The Astrophysical Journal}\ }\textbf {\bibinfo {volume} {808}},\
		\bibinfo {pages} {114} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Douglas}(1977)}]{dou77}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
			{Douglas}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Origin of
				diffuse interstellar lines},}\ }\href
	{https://www.nature.com/articles/269130a0} {\bibfield  {journal} {\bibinfo
			{journal} {Nature}\ }\textbf {\bibinfo {volume} {269}},\ \bibinfo {pages}
		{130--132} (\bibinfo {year} {1977})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Fulara}\ \emph {et~al.}(1993)\citenamefont {Fulara},
		\citenamefont {Lessen}, \citenamefont {Freivogel},\ and\ \citenamefont
		{Maier}}]{ful93}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Fulara}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Lessen}},
		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Freivogel}}, \ and\
		\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Maier}},\ }\bibfield
	{title} {\enquote {\bibinfo {title} {Laboratory evidence for highly
				unsaturated hydrocarbons as carriers of some of the diffuse interstellar
				bands},}\ }\href {https://www.nature.com/articles/366439a0} {\bibfield
		{journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {366}},\
		\bibinfo {pages} {439--441} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {{Watson}}(1994)}]{wat94}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
			{{Watson}}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Homologous
					Series of Diffuse Interstellar Bands}},}\ }\href {\doibase 10.1086/175030}
	{\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical Journal}\
		}\textbf {\bibinfo {volume} {437}},\ \bibinfo {pages} {678} (\bibinfo {year}
		{1994})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Fulara}\ and\ \citenamefont
		{Krelowski}(2000)}]{ful00}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Fulara}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Krelowski}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Origin of
				diffuse interstellar bands: spectroscopic studies of their possible
				carriers},}\ }\href {\doibase https://doi.org/10.1016/S1387-6473(00)00108-1}
	{\bibfield  {journal} {\bibinfo  {journal} {New Astronomy Reviews}\ }\textbf
		{\bibinfo {volume} {44}},\ \bibinfo {pages} {581--597} (\bibinfo {year}
		{2000})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Schmidt Timothy~W.}(2005)}]{sch05}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.~G.}\
			\bibnamefont {Schmidt Timothy~W.}},\ }\bibfield  {title} {\enquote {\bibinfo
			{title} {The optical spectroscopy of extraterrestrial molecules.}}\ }\href
	{https://www.publish.csiro.au/ch/Fulltext/CH04269#R14} {\bibfield  {journal}
		{\bibinfo  {journal} {Australian Journal of Chemistry}\ }\textbf {\bibinfo
			{volume} {58}},\ \bibinfo {pages} {69--81} (\bibinfo {year}
		{2005})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Millar}, \citenamefont {Walsh},\ and\ \citenamefont
		{Field}(2017)}]{mil17}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~J.}\ \bibnamefont
			{Millar}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Walsh}}, \
		and\ \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Field}},\
	}\bibfield  {title} {\enquote {\bibinfo {title} {Negative ions in space},}\
	}\href {\doibase 10.1021/acs.chemrev.6b00480} {\bibfield  {journal} {\bibinfo
			{journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo
		{pages} {1765--1795} (\bibinfo {year} {2017})},\ \bibinfo {note} {pMID:
		28112897}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {McCarthy}\ \emph {et~al.}(2006)\citenamefont
		{McCarthy}, \citenamefont {Gottlieb}, \citenamefont {Gupta},\ and\
		\citenamefont {Thaddeus}}]{mcc06}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~C.}\ \bibnamefont
			{McCarthy}}, \bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont
			{Gottlieb}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Gupta}}, \
		and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\
	}\bibfield  {title} {\enquote {\bibinfo {title} {{Laboratory and Astronomical
					Identification of the Negative Molecular Ion C$_6$H$^-$}},}\ }\href {\doibase
		10.1086/510238} {\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical
				Journal}\ }\textbf {\bibinfo {volume} {652}},\ \bibinfo {pages} {L141--L144}
		(\bibinfo {year} {2006})}\BibitemShut {NoStop}%
	\bibitem [{\citenamefont {Cernicharo}\ \emph {et~al.}(2007)\citenamefont
		{Cernicharo}, \citenamefont {Gu\'elin}, \citenamefont {Ag\'undez},
		\citenamefont {Kawaguchi}, \citenamefont {McCarthy},\ and\ \citenamefont
		{Thaddeus}}]{cer07}%
	\BibitemOpen
	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
			{Cernicharo}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
			{Gu\'elin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ag\'undez}},
		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Kawaguchi}}, \bibinfo
		{author} {\bibfnamefont {M.}~\bibnamefont {McCarthy}}, \ and\ \bibinfo
		{author} {\bibfnamefont {P.}~\bibnamefont {Thaddeus}},\ }\bibfield  {title}
